---
output:
  pdf_document: default
  html_document: default
---
in---
title: "UNM05"
output: pdf_document
date: "2023-07-03"
---

```{r setup, include = FALSE}
library(tidyverse)
library(afex)
library(BayesFactor)
library(apa)
#library("emmeans")
library("writexl")
load("UNM05_proc_data.RData")

# function to force scientific formatting of numbers (used for large BFs)
changeSciNot <- function(n) {
  output <- format(n, scientific = TRUE, digits = 2) #Transforms the number into scientific notation even if small
  output <- sub("e", "x10^", output) #Replace e with 10^
  output <- sub("\\+0?", "", output) #Remove + symbol and leading zeros on exponent, if > 1
  output <- sub("-0?", "-", output) #Leaves - symbol but removes leading zeros on exponent, if < 1
  output <- paste0(output,"^")
  # output = strsplit(output, "^", fixed = TRUE)
  # output = paste0(output[[1]][1],"^", output[[1]][2], "^")
  output
}

# function to extract and report BFs with error %s
report_BF_and_error <- function(BF_in, sci_not = TRUE, hyp = "alt"){
  
  if (hyp == "alt") {
    BF_notation = "BF~10~ = "
  } else if (hyp == "null") {
    BF_notation = "BF~01~ = "
  }
  
  if (sci_not == TRUE) {
    BF_value = changeSciNot(extractBF(BF_in)$bf) # change to sci notation
  } else {
    BF_value = round(extractBF(BF_in)$bf,2) # otherwise round
  }
  
  paste0(BF_notation, 
         BF_value, 
         " &plusmn; ", 
         round(100*extractBF(BF_in)$error,2), 
         "%")
}

```

# Design

This was a pilot experiment in which we aimed to find the most appropriate memory test to be used after a training in which two cues are presented in each trial followed by an outcome. Only one of the cues is predictive of the outcome, whereas the other appears the same amount of times with each of the two possible outcomes. Two tests where used, one followed by the other in all cases. Test 1 consisted in presenting one of the cues saw in the training phase and a dis tractor cue that was similar to this cue. The similarity of the distractor was manipulated between-subjects, with 3 possible conditions: very subtle (only one pair of balls swapped colors), subtle (two pairs of balls swapped colors) and no subtle (the distractor is a palette-swap of the target). In test 2, the target is presented with the distractors similar to the rest of the targets, one per trial.

+----------+----------+----------+
| Training | Test1    | Test2    |
+==========+==========+==========+
| AX - O1  | A vs *a* | A vs *b* |
|          |          |          |
|          |          | A vs *x* |
|          |          |          |
|          |          | A vs *y* |
+----------+----------+----------+
| AY - O1  | B vs *b* | B vs *a* |
|          |          |          |
|          |          | B vs *x* |
|          |          |          |
|          |          | B vs *y* |
+----------+----------+----------+
| BX - 02  | X vs *x* | X vs *a* |
|          |          |          |
|          |          | X vs *b* |
|          |          |          |
|          |          | X vs *y* |
+----------+----------+----------+
| BY - O2  | Y vs *y* | Y vs *a* |
|          |          |          |
|          |          | Y vs *b* |
|          |          |          |
|          |          | Y vs *x* |
+----------+----------+----------+

# All Data
```{r, include=FALSE}
training <- filter(training, !participant %in% not_passed)
test1 <- filter(test1, !participant %in% not_passed)
test2 <- filter(test2, !participant %in% not_passed)

#Code conditions
test1 <- test1 %>%
  mutate(condition = case_when(session == 1 ~ "Very Subtle",
                                session == 2 ~ "Subtle",
                                session == 3 ~ "No subtle"))
test2 <- test2 %>%
  mutate(condition = case_when(session == 1 ~ "Very Subtle",
                                session == 2 ~ "Subtle",
                                session == 3 ~ "No subtle"))

#Create a corrected memory score column
test1 <- test1 %>%
mutate (c_mem_score = case_when(acc == 0 ~ 0, acc == 1 ~ mem_score))
test2 <- test2 %>%
mutate (c_mem_score = case_when(acc == 0 ~ 0, acc == 1 ~ mem_score))
```

## Test2
### Accuracy

```{r, include=FALSE}
test2 <- test2 %>%
  mutate(trial_type = case_when((target == 1 & distractor_test2 == 2) | (target == 2 & distractor_test2 == 1) ~ "Pt vs Pf" ,
                                (target == 5 & distractor_test2 == 6) | (target == 6 & distractor_test2 == 5) ~ "NPt vs NPf",
                                (target == 1 & (distractor_test2 == 5 | distractor_test2 == 6)) | (target == 2 & (distractor_test2 == 5 | distractor_test2 == 6)) ~ "Pt vs NPf",
                                  (target == 5 & (distractor_test2 == 1 | distractor_test2 == 2)) | (target == 6 & (distractor_test2 == 1 | distractor_test2 == 2)) ~  "NPt vs Pf"),
         congruence = case_when ((trial_type == "Pt vs Pf") | (trial_type == "NPt vs NPf") ~ "congruent",
                                 (trial_type == "Pt vs NPf") | (trial_type == "NPt vs Pf") ~ "incongruent"))
m_acc_test2 <- test2 %>%
  group_by(trial_type, condition) %>%
  summarise(mean_acc = mean(acc, na.rm = TRUE), 
            se_acc = sd(acc, na.rm = TRUE)/sqrt(length(acc)))
```
```{r, echo=FALSE}
ggplot(data = m_acc_test2) +
  geom_col(mapping = aes(x = condition, y = mean_acc, fill = trial_type), position = position_dodge2()) +
  geom_errorbar(aes(x= condition, y = mean_acc, ymin = mean_acc-se_acc, ymax = mean_acc+se_acc, group = trial_type), color = "black", width=.2,position=position_dodge(0.9)) +
  coord_cartesian(ylim = c(0, 1))+
  scale_x_discrete (name = "Group") + 
  labs(fill = "Trial type") +
  scale_y_continuous(name = "Accuracy") +
  labs(title = "Mean accuracy for each type of cue in test2 phase")+
  scale_fill_brewer(palette = "PRGn")
```
```{r, include=FALSE}
#ANOVA accuracy
acc_test2 <- test2 %>%
  group_by (pNum, session, predictiveness, congruence) %>%
  summarise(acc = mean(acc, na.rm = TRUE))
acc_test2$predictiveness <- factor(acc_test2$predictiveness)
acc_test2$congruence <- factor(acc_test2$congruence)
acc_test2$session <- factor(acc_test2$session)
acc_test2$pNum <- factor(acc_test2$pNum)
ANOVA_acc_test2 <- aov_car(formula = acc ~ session + Error(pNum*predictiveness*congruence), data = acc_test2)
print(ANOVA_acc_test2)
bay_ANOVA_acc_test2 <- anovaBF(formula = acc ~ session + predictiveness + congruence + pNum,
        data = data.frame(acc_test2),
        whichRandom = "pNum")
print(bay_ANOVA_acc_test2)
bay_ANOVA_acc_test2_sxp <- bay_ANOVA_acc_test2[4]/bay_ANOVA_acc_test2[3]
print(bay_ANOVA_acc_test2_sxp)
bay_ANOVA_acc_test2_pxc <- bay_ANOVA_acc_test2[13]/bay_ANOVA_acc_test2[7]
print(bay_ANOVA_acc_test2_pxc)
bay_ANOVA_acc_test2_sxc <- bay_ANOVA_acc_test2[10]/bay_ANOVA_acc_test2[6]
print(bay_ANOVA_acc_test2_sxc)
bay_ANOVA_acc_test2_sxpxc <- bay_ANOVA_acc_test2[18]/bay_ANOVA_acc_test2[17]
print(bay_ANOVA_acc_test2_sxpxc)
```

There are no differences in accuracy in Test 2, confirmed by the ANOVA (Group: `r apa(ANOVA_acc_test2, effect = "session")`, Predictiveness: `r apa(ANOVA_acc_test2, effect = "predictiveness")`; Congruence: `r apa(ANOVA_acc_test2, effect = "congruence")`;  GroupxPredictiveness `r apa(ANOVA_acc_test2, effect = "session:predictiveness")`; PredictivenessxCongruence: `r apa(ANOVA_acc_test2, effect = "predictiveness:congruence")`; GroupxCongruence: `r apa(ANOVA_acc_test2, effect = "session:congruence")`; GroupxPredictivenessxCongruence: `r apa(ANOVA_acc_test2, effect = "session:predictiveness:congruence")`). Bayesian evidence was moderate for the null hypothesis for Predictiveness, Congruence, PredictivenessxCongruence, GroupxCongruence, and GroupxPredictivenessxCongruence (Predictiveness: `r report_BF_and_error(bay_ANOVA_acc_test2[2])`; Congruence `r report_BF_and_error(bay_ANOVA_acc_test2[5])`, PredictivenessxCongruence:`r report_BF_and_error(bay_ANOVA_acc_test2_pxc[1])`; GroupxCongruence: `r report_BF_and_error(bay_ANOVA_acc_test2_sxc[1])`; GroupxPredictivenessxCongruence: `r report_BF_and_error(bay_ANOVA_acc_test2_sxpxc[1])`), and strong for the Group and GroupxPredictiveness interaction (`r report_BF_and_error(bay_ANOVA_acc_test2[1])`; `r report_BF_and_error(bay_ANOVA_acc_test2_sxp[1])`, respectively).

### Memory Score (hits x1, errors x0)
```{r, include=FALSE}
#plot test2 mem_score but take out the errors
c_m_mem_test2 <- test2 %>%
  group_by(trial_type, condition) %>%
  summarise(mean_mem_score = mean(c_mem_score, na.rm = TRUE), 
            se_mem_score = sd(c_mem_score, na.rm = TRUE)/sqrt(length(c_mem_score)))
```
```{r, echo=FALSE}
ggplot(data = c_m_mem_test2) +
  geom_col(mapping = aes(x = condition, y = mean_mem_score, fill = trial_type), position = position_dodge2()) +
  geom_errorbar(aes(x= condition, y = mean_mem_score, ymin = mean_mem_score-se_mem_score, ymax = mean_mem_score+se_mem_score, group = trial_type), color = "black", width=.2,position=position_dodge(0.9)) +
  scale_x_discrete (name = "Group") + 
  labs(fill = "Trial type") +
  scale_y_continuous(name = "Memory score") +
  labs(title = "Mean memory score for each type of cue in test2 phase")+
  scale_fill_brewer(palette = "PRGn")
```
```{r, include=FALSE}
#ANOVA mem_score
c_mem_score_test2 <- test2 %>%
  group_by (pNum, session, predictiveness, congruence) %>%
  summarise(mem_score = mean(c_mem_score, na.rm = TRUE))
c_mem_score_test2$predictiveness <- factor(c_mem_score_test2$predictiveness)
c_mem_score_test2$congruence <- factor(c_mem_score_test2$congruence)
c_mem_score_test2$session <- factor(c_mem_score_test2$session)
c_mem_score_test2$pNum <- factor(c_mem_score_test2$pNum)
c_ANOVA_mem_score_test2 <- aov_car(formula = mem_score ~ session + Error(pNum*predictiveness*congruence), data = c_mem_score_test2)
print(c_ANOVA_mem_score_test2)
c_bay_ANOVA_mem_score_test2 <- anovaBF(formula = mem_score ~ session + predictiveness + congruence + pNum,
        data = data.frame(c_mem_score_test2),
        whichRandom = "pNum")
print(c_bay_ANOVA_mem_score_test2)
c_bay_ANOVA_mem_score_test2_sxp <- c_bay_ANOVA_mem_score_test2[4]/c_bay_ANOVA_mem_score_test2[3]
print(c_bay_ANOVA_mem_score_test2_sxp)
c_bay_ANOVA_mem_score_test2_pxc <- c_bay_ANOVA_mem_score_test2[13]/c_bay_ANOVA_mem_score_test2[7]
print(c_bay_ANOVA_mem_score_test2_pxc)
c_bay_ANOVA_mem_score_test2_sxc <- c_bay_ANOVA_mem_score_test2[10]/c_bay_ANOVA_mem_score_test2[6]
print(c_bay_ANOVA_mem_score_test2_sxc)
c_bay_ANOVA_mem_score_test2_sxpxc <- c_bay_ANOVA_mem_score_test2[18]/c_bay_ANOVA_mem_score_test2[17]
print(c_bay_ANOVA_mem_score_test2_sxpxc)
```

The only significant differences were due to the main effect of Predictiveness (`r apa(c_ANOVA_mem_score_test2, effect = "predictiveness")`, `r report_BF_and_error(c_bay_ANOVA_mem_score_test2[2])`), being the bayesian evidence strong for the alternative hypothesis. No other significant effects were found (Group: `r apa(c_ANOVA_mem_score_test2, effect = "session")`, Congruence: `r apa(c_ANOVA_mem_score_test2, effect = "congruence")`;  GroupxPredictiveness `r apa(c_ANOVA_mem_score_test2, effect = "session:predictiveness")`; PredictivenessxCongruence: `r apa(c_ANOVA_mem_score_test2, effect = "predictiveness:congruence")`; GroupxCongruence: `r apa(c_ANOVA_mem_score_test2, effect = "session:congruence")`; GroupxPredictivenessxCongruence: `r apa(c_ANOVA_mem_score_test2, effect = "session:predictiveness:congruence")`). Bayesian evidence was moderate for the null hypothesis for all other effects  (Group: `r report_BF_and_error(c_bay_ANOVA_mem_score_test2[1])`; Congruence `r report_BF_and_error(c_bay_ANOVA_mem_score_test2[5])`; GroupxPredictiveness: `r report_BF_and_error(c_bay_ANOVA_mem_score_test2_sxp[1])`; PredictivenessxCongruence:`r report_BF_and_error(c_bay_ANOVA_mem_score_test2_pxc[1])`; GroupxCongruence: `r report_BF_and_error(c_bay_ANOVA_mem_score_test2_sxc[1])`), except for the three way interaction, in which it was strong (`r report_BF_and_error(c_bay_ANOVA_mem_score_test2_sxpxc[1])`).

# Very subtle test
## Test2
### Accuracy

```{r, include=FALSE}
test2_s1 <- filter(test2, session == 1) 
```
```{r, include=FALSE}
#ANOVA mem_score
acc_test2_s1 <- test2_s1 %>%
  group_by (pNum, predictiveness, congruence) %>%
  summarise(acc = mean(acc, na.rm = TRUE))
acc_test2_s1$predictiveness <- factor(acc_test2_s1$predictiveness)
acc_test2_s1$congruence <- factor(acc_test2_s1$congruence)
acc_test2_s1$pNum <- factor(acc_test2_s1$pNum)
ANOVA_acc_test2_s1 <- aov_car(formula = acc ~ Error(pNum*predictiveness*congruence), data = acc_test2_s1)
print(ANOVA_acc_test2_s1)
bay_ANOVA_acc_test2_s1 <- anovaBF(formula = acc ~ predictiveness + congruence + pNum,
        data = data.frame(acc_test2_s1),
        whichRandom = "pNum")
print(bay_ANOVA_acc_test2_s1)
bay_ANOVA_acc_test2_s1_int <- bay_ANOVA_acc_test2_s1[4]/bay_ANOVA_acc_test2_s1[3]
print(bay_ANOVA_acc_test2_s1_int)
```

There was not a significant effect of the Predictiveness (`r apa(ANOVA_acc_test2_s1, effect = "predictiveness")`, `r report_BF_and_error(bay_ANOVA_acc_test2_s1[1])`), with anecdotal bayesian evidence in favor of the null hypothesis; nor of congruence (`r apa(ANOVA_acc_test2_s1, effect = "congruence")`, `r report_BF_and_error(bay_ANOVA_acc_test2_s1[2])`) neither of the interaction (`r apa(ANOVA_acc_test2_s1, effect = "congruence:predictiveness")`, `r report_BF_and_error(bay_ANOVA_acc_test2_s1_int[1])`), both showing moderate bayesian evidence in favor of the null hypothesis. 

### Memory score

```{r, include=FALSE}
#t test mem_score
mem_score_test2_s1 <- test2_s1 %>%
  group_by (pNum, predictiveness, congruence) %>%
  summarise(mem_score = mean(mem_score, na.rm = TRUE))
mem_score_test2_s1$predictiveness <- factor(mem_score_test2_s1$predictiveness)
mem_score_test2_s1$congruence <- factor(mem_score_test2_s1$congruence)
mem_score_test2_s1$pNum <- factor(mem_score_test2_s1$pNum)
ANOVA_mem_score_test2_s1 <- aov_car(formula = mem_score ~ Error(pNum*predictiveness*congruence), data = mem_score_test2_s1)
print(ANOVA_mem_score_test2_s1)
bay_ANOVA_mem_score_test2_s1 <- anovaBF(formula = mem_score ~ predictiveness + congruence + pNum,
        data = data.frame(mem_score_test2_s1),
        whichRandom = "pNum")
print(bay_ANOVA_mem_score_test2_s1)
bay_ANOVA_mem_score_test2_s1_int <- bay_ANOVA_mem_score_test2_s1[4]/bay_ANOVA_mem_score_test2_s1[3]
print(bay_ANOVA_mem_score_test2_s1_int)
```

There was a significant effect of the predictiveness (`r apa(ANOVA_mem_score_test2_s1, effect = "predictiveness")`, `r report_BF_and_error(bay_ANOVA_mem_score_test2_s1[1])`), with strong bayesian evidence in favor of the alternative hypothesis. However, there was not and effect of congruence (`r apa(ANOVA_mem_score_test2_s1, effect = "congruence")`, `r report_BF_and_error(bay_ANOVA_mem_score_test2_s1[2])`) neither of the interaction (`r apa(ANOVA_mem_score_test2_s1, effect = "congruence:predictiveness")`, `r report_BF_and_error(bay_ANOVA_mem_score_test2_s1_int[1])`), both showing moderate bayesian evidence in favor of the null hypothesis.

### Corrected memory score (hits x1, erros x0)
```{r, include=FALSE}
#t test mem_score
c_mem_score_test2_s1 <- test2_s1 %>%
  group_by (pNum, predictiveness, congruence) %>%
  summarise(mem_score = mean(c_mem_score, na.rm = TRUE))
c_mem_score_test2_s1$predictiveness <- factor(c_mem_score_test2_s1$predictiveness)
c_mem_score_test2_s1$congruence <- factor(c_mem_score_test2_s1$congruence)
c_mem_score_test2_s1$pNum <- factor(c_mem_score_test2_s1$pNum)
ANOVA_c_mem_score_test2_s1 <- aov_car(formula = mem_score ~ Error(pNum*predictiveness*congruence), data = c_mem_score_test2_s1)
print(ANOVA_c_mem_score_test2_s1)
bay_ANOVA_c_mem_score_test2_s1 <- anovaBF(formula = mem_score ~ predictiveness + congruence + pNum,
        data = data.frame(c_mem_score_test2_s1),
        whichRandom = "pNum")
print(bay_ANOVA_c_mem_score_test2_s1)
bay_ANOVA_c_mem_score_test2_s1_int <- bay_ANOVA_c_mem_score_test2_s1[4]/bay_ANOVA_c_mem_score_test2_s1[3]
print(bay_ANOVA_c_mem_score_test2_s1_int)
```

There was a significant effect of the predictiveness (`r apa(ANOVA_c_mem_score_test2_s1, effect = "predictiveness")`, `r report_BF_and_error(bay_ANOVA_c_mem_score_test2_s1[1])`), with extreme bayesian evidence in favor of the alternative hypothesis. However, there was not and effect of congruence (`r apa(ANOVA_c_mem_score_test2_s1, effect = "congruence")`, `r report_BF_and_error(bay_ANOVA_c_mem_score_test2_s1[2])`) neither of the interaction (`r apa(ANOVA_c_mem_score_test2_s1, effect = "congruence:predictiveness")`, `r report_BF_and_error(bay_ANOVA_c_mem_score_test2_s1_int[1])`), congruence showing moderate bayesian evidence in favor of the null hypothesis and the interaction showing anecdotal null evidence.

# Subtle test
## Test2
### Accuracy

```{r, include=FALSE}
test2_s2 <- filter(test2, session == 2)
```
```{r, include=FALSE}
#ANOVA mem_score
acc_test2_s2 <- test2_s2 %>%
  group_by (pNum, predictiveness, congruence) %>%
  summarise(acc = mean(acc, na.rm = TRUE))
acc_test2_s2$predictiveness <- factor(acc_test2_s2$predictiveness)
acc_test2_s2$congruence <- factor(acc_test2_s2$congruence)
acc_test2_s2$pNum <- factor(acc_test2_s2$pNum)
ANOVA_acc_test2_s2 <- aov_car(formula = acc ~ Error(pNum*predictiveness*congruence), data = acc_test2_s2)
print(ANOVA_acc_test2_s2)
bay_ANOVA_acc_test2_s2 <- anovaBF(formula = acc ~ predictiveness + congruence + pNum,
        data = data.frame(acc_test2_s2),
        whichRandom = "pNum")
print(bay_ANOVA_acc_test2_s2)
bay_ANOVA_acc_test2_s2_int <- bay_ANOVA_acc_test2_s2[4]/bay_ANOVA_acc_test2_s2[3]
print(bay_ANOVA_acc_test2_s2_int)
```

There was not a significant effect of the predictiveness (`r apa(ANOVA_acc_test2_s2, effect = "predictiveness")`, `r report_BF_and_error(bay_ANOVA_acc_test2_s2[1])`), nor of congruence (`r apa(ANOVA_acc_test2_s2, effect = "congruence")`, `r report_BF_and_error(bay_ANOVA_acc_test2_s2[2])`) neither of the interaction (`r apa(ANOVA_acc_test2_s2, effect = "congruence:predictiveness")`, `r report_BF_and_error(bay_ANOVA_acc_test2_s2_int[1])`), all showing moderate bayesian evidence in favor of the null hypothesis. 

### Memory score
```{r, include=FALSE}
#t test mem_score
mem_score_test2_s2 <- test2_s2 %>%
  group_by (pNum, predictiveness, congruence) %>%
  summarise(mem_score = mean(mem_score, na.rm = TRUE))
mem_score_test2_s2$predictiveness <- factor(mem_score_test2_s2$predictiveness)
mem_score_test2_s2$congruence <- factor(mem_score_test2_s2$congruence)
mem_score_test2_s2$pNum <- factor(mem_score_test2_s2$pNum)
ANOVA_mem_score_test2_s2 <- aov_car(formula = mem_score ~ Error(pNum*predictiveness*congruence), data = mem_score_test2_s2)
print(ANOVA_mem_score_test2_s2)
bay_ANOVA_mem_score_test2_s2 <- anovaBF(formula = mem_score ~ predictiveness + congruence + pNum,
        data = data.frame(mem_score_test2_s2),
        whichRandom = "pNum")
print(bay_ANOVA_mem_score_test2_s2)
bay_ANOVA_mem_score_test2_s2_int <- bay_ANOVA_mem_score_test2_s2[4]/bay_ANOVA_mem_score_test2_s2[3]
print(bay_ANOVA_mem_score_test2_s2_int)
```

There was not significant effect of the predictiveness (`r apa(ANOVA_mem_score_test2_s2, effect = "predictiveness")`, `r report_BF_and_error(bay_ANOVA_mem_score_test2_s2[1])`), nor of congruence (`r apa(ANOVA_mem_score_test2_s2, effect = "congruence")`, `r report_BF_and_error(bay_ANOVA_mem_score_test2_s2[2])`) neither of the interaction (`r apa(ANOVA_mem_score_test2_s2, effect = "congruence:predictiveness")`, `r report_BF_and_error(bay_ANOVA_mem_score_test2_s2_int[1])`), all showing moderate bayesian evidence in favor of the null hypothesis.

### Corrected memory score (hits x1, erros x0)
```{r, include=FALSE}
#t test mem_score
c_mem_score_test2_s2 <- test2_s2 %>%
  group_by (pNum, predictiveness, congruence) %>%
  summarise(mem_score = mean(c_mem_score, na.rm = TRUE))
c_mem_score_test2_s2$predictiveness <- factor(c_mem_score_test2_s2$predictiveness)
c_mem_score_test2_s2$congruence <- factor(c_mem_score_test2_s2$congruence)
c_mem_score_test2_s2$pNum <- factor(c_mem_score_test2_s2$pNum)
ANOVA_c_mem_score_test2_s2 <- aov_car(formula = mem_score ~ Error(pNum*predictiveness*congruence), data = c_mem_score_test2_s2)
print(ANOVA_c_mem_score_test2_s2)
bay_ANOVA_c_mem_score_test2_s2 <- anovaBF(formula = mem_score ~ predictiveness + congruence + pNum,
        data = data.frame(c_mem_score_test2_s2),
        whichRandom = "pNum")
print(bay_ANOVA_c_mem_score_test2_s2)
bay_ANOVA_c_mem_score_test2_s2_int <- bay_ANOVA_c_mem_score_test2_s2[4]/bay_ANOVA_c_mem_score_test2_s2[3]
print(bay_ANOVA_c_mem_score_test2_s2_int)
```

There was not a significant effect of the predictiveness (`r apa(ANOVA_c_mem_score_test2_s2, effect = "predictiveness")`, `r report_BF_and_error(bay_ANOVA_c_mem_score_test2_s2[1])`), nor of congruence (`r apa(ANOVA_c_mem_score_test2_s2, effect = "congruence")`, `r report_BF_and_error(bay_ANOVA_c_mem_score_test2_s2[2])`) neither of the interaction (`r apa(ANOVA_c_mem_score_test2_s2, effect = "congruence:predictiveness")`, `r report_BF_and_error(bay_ANOVA_c_mem_score_test2_s2_int[1])`). Predictiveness showed anecdotal bayesian evidence in favor of the null hypothesis, whereas congruence and interaction showed moderate.

# No subtle test
## Test2
### Accuracy

```{r, include=FALSE}
test2_s3 <- filter(test2, session == 3) 
```
```{r, include=FALSE}
#ANOVA mem_score
acc_test2_s3 <- test2_s3 %>%
  group_by (pNum, predictiveness, congruence) %>%
  summarise(acc = mean(acc, na.rm = TRUE))
acc_test2_s3$predictiveness <- factor(acc_test2_s3$predictiveness)
acc_test2_s3$congruence <- factor(acc_test2_s3$congruence)
acc_test2_s3$pNum <- factor(acc_test2_s3$pNum)
ANOVA_acc_test2_s3 <- aov_car(formula = acc ~ Error(pNum*predictiveness*congruence), data = acc_test2_s3)
print(ANOVA_acc_test2_s3)
bay_ANOVA_acc_test2_s3 <- anovaBF(formula = acc ~ predictiveness + congruence + pNum,
        data = data.frame(acc_test2_s3),
        whichRandom = "pNum")
print(bay_ANOVA_acc_test2_s3)
bay_ANOVA_acc_test2_s3_int <- bay_ANOVA_acc_test2_s3[4]/bay_ANOVA_acc_test2_s3[3]
print(bay_ANOVA_acc_test2_s3_int)
```

There was not a significant effect of the predictiveness (`r apa(ANOVA_acc_test2_s3, effect = "predictiveness")`, `r report_BF_and_error(bay_ANOVA_acc_test2_s3[1])`), nor of congruence (`r apa(ANOVA_acc_test2_s3, effect = "congruence")`, `r report_BF_and_error(bay_ANOVA_acc_test2_s3[2])`) neither of the interaction (`r apa(ANOVA_acc_test2_s3, effect = "congruence:predictiveness")`, `r report_BF_and_error(bay_ANOVA_acc_test2_s3_int[1])`), all showing moderate bayesian evidence in favor of the null hypothesis. 

### Memory score

```{r, include=FALSE}
#t test mem_score
mem_score_test2_s3 <- test2_s3 %>%
  group_by (pNum, predictiveness, congruence) %>%
  summarise(mem_score = mean(mem_score, na.rm = TRUE))
mem_score_test2_s3$predictiveness <- factor(mem_score_test2_s3$predictiveness)
mem_score_test2_s3$congruence <- factor(mem_score_test2_s3$congruence)
mem_score_test2_s3$pNum <- factor(mem_score_test2_s3$pNum)
ANOVA_mem_score_test2_s3 <- aov_car(formula = mem_score ~ Error(pNum*predictiveness*congruence), data = mem_score_test2_s3)
print(ANOVA_mem_score_test2_s3)
bay_ANOVA_mem_score_test2_s3 <- anovaBF(formula = mem_score ~ predictiveness + congruence + pNum,
        data = data.frame(mem_score_test2_s3),
        whichRandom = "pNum")
print(bay_ANOVA_mem_score_test2_s3)
bay_ANOVA_mem_score_test2_s3_int <- bay_ANOVA_mem_score_test2_s3[4]/bay_ANOVA_mem_score_test2_s3[3]
print(bay_ANOVA_mem_score_test2_s3_int)
```

There was not significant effect of the predictiveness (`r apa(ANOVA_mem_score_test2_s3, effect = "predictiveness")`, `r report_BF_and_error(bay_ANOVA_mem_score_test2_s3[1])`), nor of congruence (`r apa(ANOVA_mem_score_test2_s3, effect = "congruence")`, `r report_BF_and_error(bay_ANOVA_mem_score_test2_s3[2])`) neither of the interaction (`r apa(ANOVA_mem_score_test2_s3, effect = "congruence:predictiveness")`, `r report_BF_and_error(bay_ANOVA_mem_score_test2_s3_int[1])`), all showing moderate bayesian evidence in favor of the null hypothesis.

### Corrected memory score (hits x1, erros x0)

```{r, include=FALSE}
#t test mem_score
c_mem_score_test2_s3 <- test2_s3 %>%
  group_by (pNum, predictiveness, congruence) %>%
  summarise(mem_score = mean(c_mem_score, na.rm = TRUE))
c_mem_score_test2_s3$predictiveness <- factor(c_mem_score_test2_s3$predictiveness)
c_mem_score_test2_s3$congruence <- factor(c_mem_score_test2_s3$congruence)
c_mem_score_test2_s3$pNum <- factor(c_mem_score_test2_s3$pNum)
ANOVA_c_mem_score_test2_s3 <- aov_car(formula = mem_score ~ Error(pNum*predictiveness*congruence), data = c_mem_score_test2_s3)
print(ANOVA_c_mem_score_test2_s3)
bay_ANOVA_c_mem_score_test2_s3 <- anovaBF(formula = mem_score ~ predictiveness + congruence + pNum,
        data = data.frame(c_mem_score_test2_s3),
        whichRandom = "pNum")
print(bay_ANOVA_c_mem_score_test2_s3)
bay_ANOVA_c_mem_score_test2_s3_int <- bay_ANOVA_c_mem_score_test2_s3[4]/bay_ANOVA_c_mem_score_test2_s3[3]
print(bay_ANOVA_c_mem_score_test2_s3_int)
```

There was not a significant effect of the predictiveness (`r apa(ANOVA_c_mem_score_test2_s3, effect = "predictiveness")`, `r report_BF_and_error(bay_ANOVA_c_mem_score_test2_s3[1])`), nor of congruence (`r apa(ANOVA_c_mem_score_test2_s3, effect = "congruence")`, `r report_BF_and_error(bay_ANOVA_c_mem_score_test2_s3[2])`) neither of the interaction (`r apa(ANOVA_c_mem_score_test2_s3, effect = "congruence:predictiveness")`, `r report_BF_and_error(bay_ANOVA_c_mem_score_test2_s3_int[1])`). All effects showed moderate bayesian evidence in favor of the null hypothesis.
